Bluetooth Loader for mruby Bytecode \\ in Multiple Virtual Machine Environment

### 2016-04-26 EMSOFT2016/blind.tex
update

\title{Bluetooth Loader for mruby Bytecode \\ in Multi-VM Environment}
\numberofauthors{3}
\author{
\alignauthor
Takuro Yamamoto\\
    \affaddr{Graduate School of Engineering Science, Osaka University}\\
    \affaddr{Osaka, JAPAN}\\
       % \affaddr{Wallamaloo, New Zealand}\\
       % \email{trovato@corporation.com}
\alignauthor
Hiroshi Oyama\\
    \affaddr{OKUMA Corporation}\\
    \affaddr{Aichi, JAPAN}\\
       % \affaddr{Dublin, Ohio 43017-6221}\\
       % \email{webmaster@marysville-ohio.com}
\alignauthor
Takuya Azumi\\
    \affaddr{Graduate School of Engineering Science, Osaka University}\\
    \affaddr{Osaka, JAPAN}\\
       % \affaddr{Hekla, Iceland}\\
       % \email{larst@affiliation.org}
}
%\author{Takuro Yamamoto}
%\date{\today}

@@

%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Acknowledgement}
This work was supported by JSPS KAKENHI Grant Number 15H05305.
We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrv}
\bibliography{ref}

>>>>

\title{Bluetooth Loader for mruby Bytecode \\ in Multiple Virtual Machine Environment}
\numberofauthors{3}
% \author{
% \alignauthor
% Takuro Yamamoto\\
%     \affaddr{Graduate School of Engineering Science, Osaka University}\\
%     \affaddr{Osaka, JAPAN}\\
%        % \affaddr{Wallamaloo, New Zealand}\\
%        % \email{trovato@corporation.com}
% \alignauthor
% Hiroshi Oyama\\
%     \affaddr{OKUMA Corporation}\\
%     \affaddr{Aichi, JAPAN}\\
%        % \affaddr{Dublin, Ohio 43017-6221}\\
%        % \email{webmaster@marysville-ohio.com}
% \alignauthor
% Takuya Azumi\\
%     \affaddr{Graduate School of Engineering Science, Osaka University}\\
%     \affaddr{Osaka, JAPAN}\\
%        % \affaddr{Hekla, Iceland}\\
%        % \email{larst@affiliation.org}
% }
%\author{Takuro Yamamoto}
%\date{\today}

@@

%%%%%%%%%%%% Acknowledgement %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Acknowledgement}
% This work was supported by JSPS KAKENHI Grant Number 15H05305.
% We would like to thank Takuya Ishikawa, Hiroshi Mimaki, and Kazuaki Tanaka for supporting this research.
%%%%%%%%%%%% Reference %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{abbrv}
\bibliography{blind}
